Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-03 MS/ms.Rmd
More writing. Fixing Table...not clear why i was added...my mistake

# I'm just listing a bunch here, but we should think about what we want to include. Here's an example of how we can make a table with all equations. Fun! Really useful website here: https://math.meta.stackexchange.com/questions/5020/mathjax-basic-tutorial-and-quick-reference. Something wrong with character coding when rendering word document. Has to do with the log odds ratio equation. Renders fine in html, but just stops when word
names <- c("Mean",
           "Log Standard deviation. lnSD",
           "Log Response Ratio, lnRR",
           # leave this for now??? - we introduce this later
           "Standardised Mean Difference, SMD",
           "Zr (Fisher Trasnformaiton of \n correlation Coefficient, r)")
           #"Log Odds Ratio",
           #"")

@@

eqns_yi <- c("M_i",
             "\\ln{SD_i} + \\frac{1}{2(N_i - 1)}",
             # Senior will have a better version but this is good for now
             "\\ln \\left( \\frac{M_{i1}}{M_{i2}}\\right)",
             "\\frac{\\left( X_{i2} - X_{i1}\\right)}{SD_{p}}J",
             # we need to spell out SD_p somewhere
             "\\frac{1}{2}log\\left(\\frac{1+r_{i}}{1-r_{i}}\\right)")
             #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
             #"- log\\left(\\frac{y_{i1}+0.5}{n_{i1}-y_{i1}+0.5}\\right)")

# Just placeholders for now
eqns_vi <- c("\\frac{SD_{i}^2}{N_{i}}",
             "\\frac{1}{2(N_i - 1)}",
             "\\frac{N_{1i} + N_{2i}}{N_{1i}N_{2i}} + \\frac{SMD^2}{2(N_{1i} + N_{2i})}",
             "\\frac{SD_{1i}} {M^2_{1i}N_{1i}} + \\frac{SD_{2i}} {M^2_{2i}N_{2i}}",
             # see my commenst
             "\\frac{1}{N_i - 3}")
             #"\\frac{s_{i}^2}{n_{i}}",
             #"")

@@

>>>>

# I'm just listing a bunch here, but we should think about what we want to include. Here's an example of how we can make a table with all equations. Fun! Really useful website here: https://math.meta.stackexchange.com/questions/5020/mathjax-basic-tutorial-and-quick-reference. Something wrong with character coding when rendering word document. Has to do with the log odds ratio equation. Renders fine in html, but just stops when word
names <- c("Mean",
           "Log Standard deviation, lnSD",
           "Log Response Ratio, lnRR",
           # leave this for now??? - we introduce this later
           "Standardised Mean Difference, SMD",
           "Zr (Fisher Trasnformaiton of \n correlation Coefficient, r)")
           #"Log Odds Ratio",
           #"")

@@

eqns_yi <- c("M",
             "\\ln{SD} + \\frac{1}{2(N - 1)}",
             # Senior will have a better version but this is good for now
             "\\ln \\left( \\frac{M_{1}}{M_{2}}\\right)",
             "\\frac{\\left( X_{2} - X_{1}\\right)}{SD_{p}}J",
             # we need to spell out SD_p somewhere
             "\\frac{1}{2}log\\left(\\frac{1+r}{1-r}\\right)")
             #"log\\left(\\frac{y_{i2}+0.5}{n_{i2}-y_{i2}+0.5}\\right) ",
             #"- log\\left(\\frac{y_{i1}+0.5}{n_{i1}-y_{i1}+0.5}\\right)")

# Just placeholders for now
eqns_vi <- c("\\frac{SD^2}{N}",
             "\\frac{1}{2(N - 1)}",
             "\\frac{N_{1} + N_{2}}{N_{1}N_{2}} + \\frac{SMD^2}{2(N_{1} + N_{2})}",
             "\\frac{SD_{1}} {M^2_{1}N_{1}} + \\frac{SD_{2}} {M^2_{2}N_{2}}",
             # see my commenst
             "\\frac{1}{N - 3}")
             #"\\frac{s_{i}^2}{n_{i}}",
             #"")

# Maybe add some examples for each effect size in a new column. SHould help
eg <- c("CT_{min}, CT_{max}, MR",
        "")

@@

As is clear from Table \@ref(tab:tablea) none of the effect measures control for 'nusance heterogenity'. For example, the magnitude of response between two treatment groups for lnRR or SMD might depend on just how different the tempeartures, dosages, pH or water potential applied in each treatment. Even modelling just the mean often needs to account for 'nusance heterogenity'. For example, standard metabolic rate (SMR) is tempearture dependent. As such, one needs to standardise the temperature measurement to compare across studies [@White2006; @Uyeda2017; if, of course, temperature is not of interest in of itself]. While we could of course model this explictly, this may not always be desireable. It can often be useful to standardise the effect to both ease its interpretation and simplify modelling. In Box 1 we provide readers with guidance on how comparative physiologists can apply corrections to the effect measure itself. We highlight two examples in the box focusing mainly on generality. Below, we show using a common well understood effect measure of interest to comparative physiologys, $Q_{10}$ how we can formalise a common effect size measure $lnRR$ to capture this 'nusance variation'.
